---
title       : Coursera Slidify Project
subtitle    : 
author      : Dipan Man Shrestha
job         : Civil Engineer
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : default      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Disease Prediction Using R

1. How I have created dataset ?
2. Cleaning and Rensing dataset ?
3. Data Mining
4. ML Models
5. Results

--- .class #id

## Dataset

  The data set was manually created.
  Intervied 50 different people.
  ```{r, echo=2}
    load("/home/tensor/Documents/Tutorials/R/Ninth/data/disease.RData")
    head(d1)
  ```

--- .class #id

## Data Cleaning
  
  Empty values were removed.
  
  Disease columns was casted as factor.
```{r}
    colnames(d1)
```

--- .class #id

## Ml Algorithms

  Using tm library stop word was removed.
  
  Frequency table was built based on the occurance of words.
  
  Also TF-ITF was calculated.

```{r}
    library(tm)
```

--- .class #id

## Visualization
Using diamonds dataset for visualization 

as my data points are not good.
```{r, echo=5}
library(ggplot2)
data(diamonds)
diamonds<-diamonds[sample(1:nrow(diamonds),2000),]
ggplot(diamonds, aes(carat, price))+geom_point(color="firebrick")
```
